Including EW and mixed QCD-EW corrections into PDF fits

### 2020-04-07 paper/sec-results.tex
Updated processes in Sect.3

>>>>

ERN 7 Apr: there is consensus on the fact that we should present results for the
following data sets:
\begin{itemize}
\item ATLAS high mass DY distributions, 7 TeV~\cite{Aad:2013iua} (CS);
\item CMS 2D DY distributions, 7 TeV~\cite{Chatrchyan:2013tia} (CS);
\item ATLAS top pair differential distributions ($m_{t\bar{t}}$ and $p_T^t$), 
8 TeV~\cite{Aad:2015mbv} (ERN);
\item CMS $Z$ $pT$ distributions, 13 TeV~\cite{Sirunyan:2019bzr} (ERN).
\end{itemize}

We agree not to display any LHCb measurement, given that they won't add
further value to our discussion.
Note added: we might also want to have a look at the ATLAS 2D and 3D DY 
distributions, 8 TeV~\cite{Aad:2016zzw,Aaboud:2017ffb}, if time allows 
us to do so.
